---
title: "plot running time csv"
author: "Shu Xu"
date: "3/8/2017"
output: html_document
---


```{r,warning=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
```

# RHC
## Choose the best RHC to plot the hill climbing
```{r}
data <- read.csv("../Results/Part1/RHC_btrain_run_1_iter_20000.csv", header = FALSE,sep=",")
colnames(data) <- c("time", "Accuracy_test", "Accuracy_train")
data <- subset(data, data$Accuracy_train >0)
data$iterationNumber <- seq(1:20000)
str(data)
data_plot <- ggplot(data, aes(x=iterationNumber)) + 
  #geom_smooth(aes(y = time, colour = time), method = 'loess', na.rm=TRUE) + 
  geom_smooth(aes(y = Accuracy_train, colour = "Accuracy_train"), method = 'loess', na.rm=TRUE) + 
  geom_smooth(aes(y = Accuracy_test, colour = "Accuracy_test"), method = 'loess', na.rm=TRUE) + 
  labs(title = "Accuracy per Iteration of Best RHC, one of the best traces", y = "", x="Iterations") +ylim(70,100)
data_plot
#ggsave("bestRHC.pdf")
```
## Choose the worst RHC to plot the hill climbing, local maxima
```{r}
worstRHC <- read.csv("../Results/Part1/RHC_btrain_run_5_iter_5000.csv", header = FALSE,sep=",")
colnames(worstRHC) <- c("time", "Accuracy_test", "Accuracy_train")
worstRHC <- subset(worstRHC, worstRHC$Accuracy_train >0)
worstRHC$iterationNumber <- seq(1:5000)
worstRHC_plot <- ggplot(worstRHC, aes(x=iterationNumber)) + 
  #geom_smooth(aes(y = time, colour = time), method = 'loess', na.rm=TRUE) + 
  geom_smooth(aes(y = Accuracy_train, colour = "Accuracy_train"), method = 'loess', na.rm=TRUE) + 
  geom_smooth(aes(y = Accuracy_test, colour = "Accuracy_test"), method = 'loess', na.rm=TRUE) + 
  labs(title = "Accuracy per Iteration of RHC, one of the worst traces", y = "", x="Iterations")
worstRHC_plot
#ggsave("bestRHC.pdf")
```




# SA
## good sa result
```{r}
data <- read.csv("../Results/Part1/SA_btrain_run_1_iter_20000.csv", header = FALSE,sep=",")
colnames(data) <- c("time", "Accuracy_test", "Accuracy_train")
data <- subset(data, data$Accuracy_train >0)
data$iterationNumber <- seq(1:20000)
str(data)
data_plot <- ggplot(data, aes(x=iterationNumber)) + 
  #geom_smooth(aes(y = time, colour = time), method = 'loess', na.rm=TRUE) + 
  geom_smooth(aes(y = Accuracy_train, colour = "Accuracy_train"), method = 'loess', na.rm=TRUE) + 
  geom_smooth(aes(y = Accuracy_test, colour = "Accuracy_test"), method = 'loess', na.rm=TRUE) + 
  labs(title = "Accuracy per Iteration of SA, Start temperature 1E11, cooling rate 0.95", y = "", x="Iterations")
data_plot
#ggsave("bestRHC.pdf")
```


## SA starting temperature is not good
```{r}
data <- read.csv("../Results/Part1/SA_btrain_run_2_iter_10000.csv", header = FALSE,sep=",")
colnames(data) <- c("time", "Accuracy_test", "Accuracy_train")
data <- subset(data, data$Accuracy_train >0)
data$iterationNumber <- seq(1:10000)
str(data)
data_plot <- ggplot(data, aes(x=iterationNumber)) + 
  #geom_smooth(aes(y = time, colour = time), method = 'loess', na.rm=TRUE) + 
  geom_smooth(aes(y = Accuracy_train, colour = "Accuracy_train"), method = 'loess', na.rm=TRUE) + 
  geom_smooth(aes(y = Accuracy_test, colour = "Accuracy_test"), method = 'loess', na.rm=TRUE) + 
  labs(title = "Accuracy per Iteration of SA, Start temperature 1E11, cooling rate 1", y = "", x="Iterations")
data_plot
#ggsave("bestRHC.pdf")
```


## SA cold temperature, it is a kind of like RHC
```{r}
data <- read.csv("../Results/Part1/SA_btrain_run_5_iter_10000.csv", header = FALSE,sep=",")
colnames(data) <- c("time", "Accuracy_test", "Accuracy_train")
data <- subset(data, data$Accuracy_train >0)
data$iterationNumber <- seq(1:10000)
data_plot <- ggplot(data, aes(x=iterationNumber)) + 
  #geom_smooth(aes(y = time, colour = time), method = 'loess', na.rm=TRUE) + 
  geom_smooth(aes(y = Accuracy_train, colour = "Accuracy_train"), method = 'loess', na.rm=TRUE) + 
  geom_smooth(aes(y = Accuracy_test, colour = "Accuracy_test"), method = 'loess', na.rm=TRUE) + 
  labs(title = "Accuracy per Iteration of SA, Start temperature 200, cooling rate 0.99", y = "", x="Iterations")
data_plot
#ggsave("bestRHC.pdf")
```

## Chaotic SA cold temperature is  good
```{r}
data <- read.csv("../Results/Part1/SA_btrain_run_1_iter_1000.csv", header = FALSE,sep=",")
colnames(data) <- c("time", "Accuracy_test", "Accuracy_train")
data <- subset(data, data$Accuracy_train >0)
data$iterationNumber <- seq(1:1000)

data_plot <- ggplot(data, aes(x=iterationNumber)) + 
  #geom_smooth(aes(y = time, colour = time), method = 'loess', na.rm=TRUE) + 
  geom_point(aes(y = Accuracy_train, colour = "Accuracy_train"), size= 0.05, na.rm=TRUE) + 
  geom_point(aes(y = Accuracy_test, colour = "Accuracy_test"),   size= 0.05, na.rm=TRUE) + 
  labs(title = "Accuracy per Iteration of SA, Start temperature 1E21, cooling rate 1", y = "", x="Iterations")
data_plot
#ggsave("bestRHC.pdf")
```


```{r}
data <- read.csv("../Results/Part1/SA_btrain_run_2_iter_10000.csv", header = FALSE,sep=",")
colnames(data) <- c("time", "Accuracy_test", "Accuracy_train")
data <- subset(data, data$Accuracy_train >0)
data$iterationNumber <- seq(1:10000)
str(data)
data_plot <- ggplot(data, aes(x=iterationNumber)) + 
  #geom_smooth(aes(y = time, colour = time), method = 'loess', na.rm=TRUE) + 
  geom_smooth(aes(y = Accuracy_train, colour = "Accuracy_train"), method = 'loess', na.rm=TRUE) + 
  geom_smooth(aes(y = Accuracy_test, colour = "Accuracy_test"), method = 'loess', na.rm=TRUE) + 
  labs(title = "Accuracy per Iteration of SA, Start temperature 1E11, cooling rate 1", y = "", x="Iterations")
data_plot
#ggsave("bestRHC.pdf")
```





# GA
## A normal GA
```{r}
data <- read.csv("../Results/Part1/GA_200_80_10_iter_20000.csv", header = FALSE,sep=",")
colnames(data) <- c("time", "Accuracy_test", "Accuracy_train")
data <- subset(data, data$Accuracy_train >0)
data$iterationNumber <- seq(1:20000)
data_plot <- ggplot(data, aes(x=iterationNumber)) + 
  #geom_smooth(aes(y = time, colour = time), method = 'loess', na.rm=TRUE) + 
  geom_smooth(aes(y = Accuracy_train, colour = "Accuracy_train"), method = 'loess', na.rm=TRUE) + 
  geom_smooth(aes(y = Accuracy_test, colour = "Accuracy_test"), method = 'loess', na.rm=TRUE) + 
  labs(title = "GA: population=200, mate=80, mutant=10", y = "", x="Iterations")
data_plot + ylim(50, 100)
#ggsave("bestRHC.pdf")
```

## comparison sample size
```{r}
data1 <- read.csv("../Results/Part1/GA_100_80_10_iter_20000.csv", header = FALSE,sep=",")
data2 <- read.csv("../Results/Part1/GA_200_80_10_iter_20000.csv", header = FALSE,sep=",")
data3 <- read.csv("../Results/Part1/GA_400_80_10_iter_20000.csv", header = FALSE,sep=",")


colnames(data1) <- c("time", "Accuracy_test", "Accuracy_train")
colnames(data2) <- c("time", "Accuracy_test", "Accuracy_train")
colnames(data3) <- c("time", "Accuracy_test", "Accuracy_train")

data1 <- subset(data1, data1$Accuracy_train >0)
data2 <- subset(data2, data2$Accuracy_train >0)
data3 <- subset(data3, data3$Accuracy_train >0)


population <- "population100"
sample2 <- "population200"
sample3 <- "population400"

data <- as.data.frame(cbind(seq(1:20000),data1$Accuracy_test,data2$Accuracy_test,data3$Accuracy_test))
colnames(data) <- c("iterationNumber",population, sample2, sample3)
data_plot <- ggplot(data, aes(x=iterationNumber)) + 
  #geom_smooth(aes(y = time, colour = time), method = 'loess', na.rm=TRUE) + 
  geom_point(aes(y = population100, colour = population), size=0.5, na.rm=TRUE) + 
  geom_point(aes(y = population200, colour = sample2), size=0.5,  na.rm=TRUE) + 
  geom_point(aes(y = population400, colour = sample3), size=0.5,  na.rm=TRUE) + 
  labs(title = "GA: population={100,200,400}, mate=80, mutant=10", y = "Accuracy of Test", x="Iterations")
data_plot 
```



## comparison mate rate
```{r}
data1 <- read.csv("../Results/Part1/GA_400_30_10_iter_20000.csv", header = FALSE,sep=",")
data2 <- read.csv("../Results/Part1/GA_400_50_10_iter_20000.csv", header = FALSE,sep=",")
data3 <- read.csv("../Results/Part1/GA_400_80_10_iter_20000.csv", header = FALSE,sep=",")


colnames(data1) <- c("time", "Accuracy_test", "Accuracy_train")
colnames(data2) <- c("time", "Accuracy_test", "Accuracy_train")
colnames(data3) <- c("time", "Accuracy_test", "Accuracy_train")

data1 <- subset(data1, data1$Accuracy_train >0)
data2 <- subset(data2, data2$Accuracy_train >0)
data3 <- subset(data3, data3$Accuracy_train >0)


mate <- "mate30"
sample2 <- "mate50"
sample3 <- "mate80"

data <- as.data.frame(cbind(seq(1:20000),data1$Accuracy_test,data2$Accuracy_test,data3$Accuracy_test))
colnames(data) <- c("iterationNumber",mate, sample2, sample3)
data_plot <- ggplot(data, aes(x=iterationNumber)) + 
  #geom_smooth(aes(y = time, colour = time), method = 'loess', na.rm=TRUE) + 
  geom_point(aes(y = mate30, colour = mate), size=0.5, na.rm=TRUE) + 
  geom_point(aes(y = mate50, colour = sample2), size=0.5,  na.rm=TRUE) + 
  geom_point(aes(y = mate80, colour = sample3), size=0.5,  na.rm=TRUE) + 
  labs(title = "GA: population=200, mate={30,50,80}, mutant=10", y = "Accuracy of Test", x="Iterations")
data_plot
#ggsave("bestRHC.pdf")
```


## comparison mutant rate

```{r}
data1 <- read.csv("../Results/Part1/GA_200_80_10_iter_20000.csv", header = FALSE,sep=",")
data2 <- read.csv("../Results/Part1/GA_200_80_30_iter_20000.csv", header = FALSE,sep=",")
data3 <- read.csv("../Results/Part1/GA_200_80_50_iter_20000.csv", header = FALSE,sep=",")


colnames(data1) <- c("time", "Accuracy_test", "Accuracy_train")
colnames(data2) <- c("time", "Accuracy_test", "Accuracy_train")
colnames(data3) <- c("time", "Accuracy_test", "Accuracy_train")

data1 <- subset(data1, data1$Accuracy_train >0)
data2 <- subset(data2, data2$Accuracy_train >0)
data3 <- subset(data3, data3$Accuracy_train >0)


mutate <- "mumate10"
sample2 <- "mumate30"
sample3 <- "mumate50"

data <- as.data.frame(cbind(seq(1:20000),data1$Accuracy_test,data2$Accuracy_test,data3$Accuracy_test))
colnames(data) <- c("iterationNumber",mutate, sample2, sample3)
data_plot <- ggplot(data, aes(x=iterationNumber)) + 
  #geom_smooth(aes(y = time, colour = time), method = 'loess', na.rm=TRUE) + 
  geom_point(aes(y = mumate10, colour = mutate), size=0.5, na.rm=TRUE) + 
  geom_point(aes(y = mumate30, colour = sample2), size=0.5, na.rm=TRUE) + 
  geom_point(aes(y = mumate50, colour = sample3), size=0.5,na.rm=TRUE) + 
  labs(title = "GA: population=200, mate=80, mutant={10,30,50}", y = "Accuracy of Test", x="Iterations")
data_plot
```


# Optimization

## Traveling Salesman

```{r}
data <- read.csv("../Results/Part2/travelingsalesman_n.csv", header = FALSE,sep=",")


result1 <- as.data.frame(cbind(data[seq(1,160, by=8),],
                              data[seq(1,160, by=8)+1,],
                              data[seq(1,160, by=8)+2,],
                              data[seq(1,160, by=8)+3,],
                              data[seq(1,160, by=8)+4,],
                              data[seq(1,160, by=8)+5,],
                              data[seq(1,160, by=8)+6,],
                              data[seq(1,160, by=8)+7,]
                              ))


colnames(result1) <- c("RHC_time","RHC_optimal" ,"SA_time","SA_optimal","GA_time","GA_optimal","MIMIC_time", "MIMIC_optimal")
result1$Number <- seq(1:20)*200
data_plot1 <- ggplot(result1,aes(x=Number)) + 
  geom_point(aes(y = SA_time, colour = "SA"), size= 1,alpha= 0.5, na.rm=TRUE) +
  geom_point(aes(y = GA_time, colour = "GA"),   size= 0.5,na.rm=TRUE) + 
  geom_point(aes(y = RHC_time, colour = "RHC"), size= 0.5, alpha = 0.5, na.rm=TRUE) + 
    geom_point(aes(y = MIMIC_time, colour = "MIMIC"), size= 0.5,  na.rm=TRUE) + 

labs(title = "The optimization of traveling salesman", y = "Training time (s)", x="Iterations (note: MIMIC Iterations/10)")

data_plot1

data_plot2 <- ggplot(result1,aes(x=Number)) +
  
  geom_smooth(aes(y = SA_optimal, colour = "SA"), method = 'loess', na.rm=TRUE) +
  geom_smooth(aes(y = GA_optimal, colour = "GA"),  method = 'loess', ,na.rm=TRUE) + 
  geom_smooth(aes(y = RHC_optimal, colour = "RHC"), method = 'loess', na.rm=TRUE) + 
    geom_smooth(aes(y = MIMIC_optimal, colour = "MIMIC"), method = 'loess', na.rm=TRUE) + 

labs(title = "The optimization of traveling salesman", y = "Optimal value", x="Iterations (note: MIMIC Iterations/10)")

data_plot2
#ggsave("bestRHC.pdf")
```












## knapsack 
```{r}
data <- as.data.frame(read.csv("../Results/Part2/knapsack_n.csv", header = FALSE,sep=","))

result1 <- as.data.frame(cbind(data[seq(1,800, by=8),],
                              data[seq(1,800, by=8)+1,],
                              data[seq(1,800, by=8)+2,],
                              data[seq(1,800, by=8)+3,],
                              data[seq(1,800, by=8)+4,],
                              data[seq(1,800, by=8)+5,],
                              data[seq(1,800, by=8)+6,],
                              data[seq(1,800, by=8)+7,]
                              ))


colnames(result1) <- c("RHC_time","RHC_optimal" ,"SA_time","SA_optimal","GA_time","GA_optimal","MIMIC_time", "MIMIC_optimal")


colnames(result1) <- c("RHC_time","RHC_optimal" ,"SA_time","SA_optimal","GA_time","GA_optimal","MIMIC_time", "MIMIC_optimal")
result1$Number <- seq(1:100)*200

data_plot1 <- ggplot(result1,aes(x=Number)) + 
  geom_point(aes(y = SA_time, colour = "SA"), size= 1,alpha= 0.5, na.rm=TRUE) +
  geom_point(aes(y = GA_time, colour = "GA"),   size= 0.5,na.rm=TRUE) + 
  geom_point(aes(y = RHC_time, colour = "RHC"), size= 0.5, alpha = 0.5, na.rm=TRUE) + 
    geom_point(aes(y = MIMIC_time, colour = "MIMIC"), size= 0.5,  na.rm=TRUE) + 

labs(title = "The optimization of knapsack", y = "Training time (s)", x="Iterations (note: MIMIC Iterations/10)")

data_plot1

data_plot2 <- ggplot(result1,aes(x=Number)) + 
      #geom_smooth(aes(y = time, colour = time), method = 'loess', na.rm=TRUE) + 

  geom_smooth(aes(y = SA_optimal, colour = "SA"), method = 'loess', na.rm=TRUE) +
  geom_smooth(aes(y = GA_optimal, colour = "GA"),  method = 'loess', ,na.rm=TRUE) + 
  geom_smooth(aes(y = RHC_optimal, colour = "RHC"), method = 'loess', na.rm=TRUE) + 
    geom_smooth(aes(y = MIMIC_optimal, colour = "MIMIC"), method = 'loess', na.rm=TRUE) + 

labs(title = "The optimization of knapsack", y = "Optimal value", x="Iterations (note: MIMIC Iterations/10)")

data_plot2
```

# continuous peaks

```{r}
data <- as.data.frame(read.csv("../Results/Part2/continuouspeaks_n.csv", header = FALSE,sep=","))

result1 <- as.data.frame(cbind(data[seq(1,800, by=8),],
                              data[seq(1,800, by=8)+1,],
                              data[seq(1,800, by=8)+2,],
                              data[seq(1,800, by=8)+3,],
                              data[seq(1,800, by=8)+4,],
                              data[seq(1,800, by=8)+5,],
                              data[seq(1,800, by=8)+6,],
                              data[seq(1,800, by=8)+7,]
                              ))


colnames(result1) <- c("RHC_time","RHC_optimal" ,"SA_time","SA_optimal","GA_time","GA_optimal","MIMIC_time", "MIMIC_optimal")
result1$Number <- seq(1:100)*200
data_plot1 <- ggplot(result1,aes(x=Number)) + 
  geom_point(aes(y = SA_time, colour = "SA"), size= 1,alpha= 0.5, na.rm=TRUE) +
  geom_point(aes(y = GA_time, colour = "GA"),   size= 0.5,na.rm=TRUE) + 
  geom_point(aes(y = RHC_time, colour = "RHC"), size= 0.5, alpha = 0.5, na.rm=TRUE) + 
    geom_point(aes(y = MIMIC_time, colour = "MIMIC"), size= 0.5,  na.rm=TRUE) + 

labs(title = "The optimization of continuous peaks (N=60, T=6)", y = "Training time (s)", x="Iterations (note: MIMIC Iterations/10)")

data_plot1

data_plot2 <- ggplot(result1,aes(x=Number)) + 
  
  geom_smooth(aes(y = SA_optimal, colour = "SA"), method = 'loess', na.rm=TRUE) +
  geom_smooth(aes(y = GA_optimal, colour = "GA"),  method = 'loess', ,na.rm=TRUE) + 
  geom_smooth(aes(y = RHC_optimal, colour = "RHC"), method = 'loess', na.rm=TRUE) + 
    geom_smooth(aes(y = MIMIC_optimal, colour = "MIMIC"), method = 'loess', na.rm=TRUE) + 

labs(title = "The optimization of continuous peaks (N=60, T=6)", y = "Optimal value", x="Iterations (note: MIMIC Iterations/10)")

data_plot2
```